On the Programmatic Generation of Reproducible Documents

### 2020-07-27 inst/jss/supplemental-material/listdown-jss.rmd
Updates.

---
documentclass: jss
author:
  - name: Michael Kane
    affiliation: Yale University
    address:
    - 60 College Street
    - New Haven, CT 06510, USA
    email: michael.kane@yale.edu
  - name: Xun (Tony) Jiang
    affiliation: Amgen Inc
    address:
    - One Amgen Center Drive
    - Thousand Oaks, CA 91320-1799, USA
    email: xunj@amgen.com
  - name: Simon Urbanek
    affiliation: The University of Aukland
    address:
    - 38 Princes Street
    - Auckland Central, Aukland 1010, NZ
    email: s.urbanek@auckland.ac.nz
title:
  formatted: "On the Programmatic Generation of Reproducible Documents"
  # If you use tex in the formatted title, also supply version without
  plain:     "On the Programmatic Generation of Reproducible Documents"
  # For running headers, if needed
  short:     "On the Programmatic Generation of Reproducible Documents"
abstract: >
  Reproducible document standards, like \proglang{R} Markdown, facilitate the programmatic creation of documents whose content is itself programmatically generated. While these documents are generally not complete in the sense that they will not include prose content, generated by an author to provide context, a narrative, etc., programmatic generation can provide substantial efficiencies for structuring and constructing documents. This paper explores the programmatic generation of reproducible by distinguishing components that can be created by computational means from those requiring human-generated prose, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting. These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network (CRAN).
keywords:
  # at least one keyword must be supplied
  formatted: [reproducibility, reproducible documents, data presentation]
  plain:     [reproducibility, reproducible documents, data presentation]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---

>>>>

---
documentclass: jss
author:
  - name: Michael Kane
    affiliation: Yale University
    address:
    - 60 College Street
    - New Haven, CT 06510, USA
    email: michael.kane@yale.edu
  - name: Xun (Tony) Jiang
    affiliation: Amgen Inc.
    address:
    - One Amgen Center Drive
    - Thousand Oaks, CA 91320-1799, USA
    email: xunj@amgen.com
  - name: Simon Urbanek
    affiliation: The University of Aukland
    address:
    - 38 Princes Street
    - Auckland Central, Aukland 1010, NZ
    email: s.urbanek@auckland.ac.nz
title:
  formatted: "On the Programmatic Generation of Reproducible Documents"
  # If you use tex in the formatted title, also supply version without
  plain:     "On the Programmatic Generation of Reproducible Documents"
  # For running headers, if needed
  short:     "On the Programmatic Generation of Reproducible Documents"
abstract: >
  Reproducible document standards, like \proglang{R} Markdown, facilitate the programmatic creation of documents whose content is itself programmatically generated. While these documents are generally not complete in the sense that they will not include prose content, generated by an author to provide context, a narrative, etc., programmatic generation can provide substantial efficiencies for structuring and constructing documents. This paper explores the programmatic generation of reproducible by distinguishing components that can be created by computational means from those requiring human-generated prose, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting. These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network (CRAN).
keywords:
  # at least one keyword must be supplied
  formatted: [reproducibility, reproducible documents, data presentation]
  plain:     [reproducibility, reproducible documents, data presentation]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---
